### 2021-12-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@d8734bb468464e922e3370b1e282b19c3a028c70 🚀

Chicco et al. (2021) - MCC maximizes other measures, other measures do
not maximize MCC, except notably when prevalence is low, or the baseline
guessing level is uncertain, which applies to networks. In this cases,
informedness should be used as a maximization criterion.

@@

\begin{figure}
\hypertarget{fig:analytics}{%
\centering
\includegraphics{figures/analytics.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). Accuracy increases with skill, but
also increases when the bias tends towards estimating \emph{fewer}
interactions. The \(F_1\) score increases with skill but also increases
when the bias tends towards estimating \emph{more} interactions; PPV
behaves in the same way. Interestingly, \(\kappa\) responds as expected
to skill (being negative whenever \(s < 0.5\)), and peaks for values of
\(b \approx 0.5\); nevertheless, the value of bias for which \(\kappa\)
is maximized in \emph{not} \(b=0.5\), but instead increases with
classifier skill. In other words, at equal skill, maximizing \(\kappa\)
would lead to select a \emph{more} biased
classifier.}\label{fig:analytics}
}
\end{figure}

@@

@@

@@

>>>>

Chicco et al. (2021) - MCC maximizes other measures, other measures do
not maximize MCC, except notably when prevalence is low, or the baseline
guessing level is uncertain, which applies to networks. In this cases,
informedness should be used as a maximization criterion. Formulating
guidelines is particularly important, because most of the litterature
existing on optimizing classifier performance in the life sciences is
focused on genomics applications (which has very specific challenges,
see a recent discussion by Whalen et al., 2021), and can give
contradictory recommendations (Boughorbel et al., 2017; Chicco \&
Jurman, 2020; Delgado \& Tibau, 2019). This points not to a defficiency
in the litterature, but rather to a need for domain-specific evaluation
of how the particular ways in which datasets are biased can affect the
performance of predictive models.

@@

\begin{figure}
\hypertarget{fig:bias}{%
\centering
\includegraphics{figures/changing-bias.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). Accuracy increases with skill, but
also increases when the bias tends towards estimating \emph{fewer}
interactions. The \(F_1\) score increases with skill but also increases
when the bias tends towards estimating \emph{more} interactions; PPV
behaves in the same way. Interestingly, \(\kappa\) responds as expected
to skill (being negative whenever \(s < 0.5\)), and peaks for values of
\(b \approx 0.5\); nevertheless, the value of bias for which \(\kappa\)
is maximized in \emph{not} \(b=0.5\), but instead increases with
classifier skill. In other words, at equal skill, maximizing \(\kappa\)
would lead to select a \emph{more} biased classifier.}\label{fig:bias}
}
\end{figure}

\hypertarget{are-the-measures-affected-by-connectance}{%
\subsection{Are the measures affected by
connectance?}\label{are-the-measures-affected-by-connectance}}

\begin{figure}
\hypertarget{fig:connectance}{%
\centering
\includegraphics{figures/changing-connectance.png}
\caption{TODO}\label{fig:connectance}
}
\end{figure}

@@

\leavevmode\hypertarget{ref-Boughorbel2017OptCla}{}%
Boughorbel, S., Jarray, F., \& El-Anbari, M. (2017). Optimal classifier
for imbalanced data using Matthews Correlation Coefficient metric.
\emph{PloS One}, \emph{12}(6), e0177678.
\url{https://doi.org/10.1371/journal.pone.0177678}

@@

\leavevmode\hypertarget{ref-Chicco2020AdvMat}{}%
Chicco, D., \& Jurman, G. (2020). The advantages of the Matthews
correlation coefficient (MCC) over F1 score and accuracy in binary
classification evaluation. \emph{BMC Genomics}, \emph{21}(1), 6.
\url{https://doi.org/10.1186/s12864-019-6413-7}

@@

\leavevmode\hypertarget{ref-Delgado2019WhyCoh}{}%
Delgado, R., \& Tibau, X.-A. (2019). Why Cohen's Kappa should be avoided
as performance measure in classification. \emph{PloS One}, \emph{14}(9),
e0222916. \url{https://doi.org/10.1371/journal.pone.0222916}
